Embedded Domain Specific Languages inside Functional Languages

### 2014-03-13 paper.tex
wibbles with english
Fixing some errors, more text.

A deeply embeeded DSL is a DSL than can have ???.
To make this concreate, consider a DSL for arithmetic,
with addition, subtraction, multiplcation, and constants.
We want to be able to {\bf run\/} this DSL. For a shallow
embedding this is trival - we just use the built in 
arithmetic. A deep embedding is where things get
interesting. Consider a data-type for our arithmetic.

@@

@@

\begin{Code}
-- Just running the function
> f 4
Add (Lit 4) (Lit 1)
-- reifing the function, using our unique E ``Var''.
> f (Var "x")
Add (Var "x") (Lit 1)   -- reified verision of the function
\end{Code}

This is remarkabile. We're run a function with 
a dummy argument (called the protypical argument)
and extracted the body of the function.

@@

However, the trick breaks down on control flow,
which is not constructive, but instead requires
answers.

\subsection{Example: Deep EDSL for Lava}

Lava programs are written as equations of recusive bindings.

>>>>

A deeply embedded DSL is a DSL than can have ???.
To make this concrete, consider a DSL for arithmetic,
with addition, subtraction, multiplication, and constants.
We want to be able to {\bf run\/} this DSL. For a shallow
embedding this is trival - we just use the built in 
arithmetic. A deep embedding is where things get
interesting. Consider a data-type for our arithmetic.

@@

About 3 main tricks; functions, recursive values, and statements.

@@

\begin{Code}
-- Just running the function
> f 4
Add (Lit 4) (Lit 1)
-- reifing the function, using our unique E ``Var''.
> f (Var "x")
Add (Var "x") (Lit 1)   -- reified version of the function
\end{Code}

This is remarkable. We're run a function with 
a dummy argument (called the protypical argument)
and extracted the body of the function.

About where is used.

\subsection{How to spot a loop}

Lava programs are written as equations of recursive bindings.
If we attempt to build a deep embedding of Lava directly,
we will get into a infinite cycle. In order to illustrate
the challenge, we will build a deep embedding of Lava,
see where it goes wrong, and fix it using a technique called
observable sharing.

First we need a structure for our Lava Language.
\begin{Code}

data Signal where
  Register :: a -> Signal a                      -> Signal a
  Mux2     :: Signal Bool -> (Signal a,Signal a) -> Signal a
  Var      :: String                             -> Signal a -- the trick

mux2 :: ...
mux2 = mux2

toSeq :: a -> Signal a
toSeq = ...
\end{Code}

@@

The Deep EDSL trick breaks down on control flow,
which is not constructive, but instead requires
directly
